### 2018-07-21 paper/security-discussion.tex
Fixes Syntastic warning

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg \cite{OTPKX} which is authenticated and provides deniability under
surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this below.)
None of the nodes can know if the previous node is the originator or not, unless 
they collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.

>>>>

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg~\cite{OTPKX} which is authenticated and provides deniability under
surveillance-state attacks.) %is both deniable and authenticated and  provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this below.)
None of the nodes can know if the previous node is the originator or not, unless 
they collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.
